Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-04-22 papers/B1555_EdgeOn/B1555_letter.tex
fix typo

As a first trail of modelling, we create a single SIE model to 
justify the performance of a simple lensing potential. Consistent with previous studies
\citep{Marlow99, Xu14}, our single elliptical potential model cannot predict flux anomaly in B1555+375. 
We then create two separate models of the lensing potential.  In the
first we treat the lens as a SIE bulge and an exponential edge-on disk
(SIE+expdisk).  In the second model the disk is represented as a very
elongated SIE component (2-SIE).  The lens system is red, with a
strong jump in flux between the F814W (roughly I) and F160W (roughly
H) bands (Fig.~\ref{fig:multiband}), so we assign a lens redshift of
$z_\ell = 1.0$ and a source redshift of $z_s =1.5$. Our steps to explore the parameter space are: 1) Apply strong priors from SHARP AO image to the edge-on disk position angle and ellipticity, and use the best-fit model of \citet{Marlow99} as the start point of the bulge component and the source position. 2) Let all parameters without priors vary to reach a temporary best-fit. 3) Start with the best-fit in step 2 and let all parameters with priors vary to reach another best-fit (also ensure this best-fit is not far from the priors). 4) Let all parameters vary to reach the final optimal model. 
The full best-fit parameters are shown in Table
2. Both of these models predict fairly matched results with the radio
observation, and the 2-SIE model has a better performance in flux
ratios. The comparison of observation and our lens modelling is given
in Figure 3 and Tables 3 \& 4.
{\bf We have not included an external shear component into our model because the constraints provided by the image positions and  fluxes would not be sufficient 
to constrain such a model. However, we note that the image not affected by dust (image C) in the Keck AO data is consistent with negligible shear (i.e. shear strength $\Gamma_s=0.002$), when modelled with the pixelized technique by \citet{V09}.}

@@

Gravitational lensing is, {\bf at present,} the most powerful tool for
studying substructure in galaxies outside of the Local Universe, and
the flux ratio anomaly systems are a key aspect of these
investigations.  However, before using the flux ratio anomaly in any
given system to investigate structure formation and the properties of
dark matter, it is critical to eliminate other possible explanations
for the difference between the observed and expected fluxes{\bf, such as propagation effects and assumptions on the mass distribution of the lens galaxy}.  
It is for this reason that much of the effort in the flux-ratio technique
has been focused on radio-loud lens systems.  At these wavelengths,
dust extinction and microlensing effects should be minimal
\citep[although see][for a rare example of radio microlensing]{K2000}.
Radio propagation effects can affect radio fluxes, as is clearly shown
in the B0128+437 system \citep{B04}.  However, these propagation
effects can be disentangled from substructure lensing because they
have well known dependencies on wavelength. \citet{KD04} examine all
eight radio loud flux anomalous lenses besides B0128=437, namely: MG
0414+0534, B0712+472, B1359+154, B1422+231, B1555+375, B1608+656,
B1933+503, and B2045+265.  They find no strong wavelength dependence
in the flux ratios of all these systems and therefore rule out radio
propagation effects as significant contributors to the observed
anomalies.

@@

\section{Conclusions}
{\bf In this letter we have taken advantage of the power of multi-wavelength high resolution data to investigate whether flux ratio anomalies could be explained by more complex smooth models for the lens galaxy mass distribution rather than substructure. Thanks to new imaging from the SHARP $K^{\prime}$ band observations of the gravitational lens system B1555+375 we have identified the existence of a previously undetected edge-on disk. By including this disk in the mass model of the lens galaxy we find a good fit for both the positions and flux ratios of the lensed images. Our results clearly demonstrate that the lack of knowledge on the lens galaxy mass distribution, combined with the limited information provided by the position of a few lensed images, can lead to improper lens models and a misinterpretation of the origin of flux ratio anomalies. 
We stress, therefore, that one should be very careful when interpreting the nature of flux ratio anomalies, as prior assumptions on the lens mass distribution are a significant source of bias. Finally, our analysis shows that in order to derive precise quantification of the substructure population and any derived properties from strongly lensed flux anomalous systems, it is crucial to have a careful estimation of non-substructure effects. In fact, even in the presence of mass substructures, the observed flux ratio anomalies could be still dominated by the complex structure of the lens galaxy.}

>>>>

As a first trail of modelling, we create a single SIE model to 
justify the performance of a simple lensing potential. Consistent with previous studies
\citep{Marlow99, Xu14}, our single elliptical potential model cannot predict flux anomaly in B1555+375. 
We then create two separate models of the lensing potential.  In the
first we treat the lens as a SIE bulge and an exponential edge-on disk
(SIE+expdisk).  In the second model the disk is represented as a very
elongated SIE component (2-SIE).  The lens system is red, with a
strong jump in flux between the F814W (roughly I) and F160W (roughly
H) bands (Fig.~\ref{fig:multiband}), so we assign a lens redshift of
$z_\ell = 1.0$ and a source redshift of $z_s =1.5$. Our steps to explore the parameter space are: (1) Apply strong priors from SHARP AO image to the edge-on disk position angle and ellipticity, and use the best-fit model of \citet{Marlow99} as the start point of the bulge component and the source position. (2) Let all parameters without priors vary to reach a temporary best-fit. (3) Start with the best-fit in step 2 and let all parameters with priors vary to reach another best-fit (also ensure this best-fit is not far from the priors). (4) Let all parameters vary to reach the final optimal model. 
The full best-fit parameters are shown in Table
2. Both of these models predict fairly matched results with the radio
observation, and the 2-SIE model has a better performance in flux
ratios. The comparison of observation and our lens modelling is given
in Figure 3 and Tables 3 \& 4.
{\bf We have not included an external shear component into our model because the constraints provided by the image positions and  fluxes would not be sufficient 
to constrain such a model. However, we note that the image not affected by dust (image C) in the Keck AO data is consistent with negligible shear (i.e. shear strength $\Gamma_s=0.002$), when modelled with the pixelized technique by \citet{V09}.}

@@

Gravitational lensing is, {\bf at present,} the most powerful tool for
studying substructure in galaxies outside of the Local Universe, and
the flux ratio anomaly systems are a key aspect of these
investigations.  However, before using the flux ratio anomaly in any
given system to investigate structure formation and the properties of
dark matter, it is critical to eliminate other possible explanations
for the difference between the observed and expected fluxes{\bf, such as propagation effects and assumptions on the mass distribution of the lens galaxy}.  
It is for this reason that much of the effort in the flux-ratio technique
has been focused on radio-loud lens systems.  At these wavelengths,
dust extinction and microlensing effects should be minimal
\citep[although see][for a rare example of radio microlensing]{K2000}.
Radio propagation effects can affect radio fluxes, as is clearly shown
in the B0128+437 system \citep{B04}.  However, these propagation
effects can be disentangled from substructure lensing because they
have well known dependencies on wavelength. \citet{KD04} examine all
eight radio loud flux anomalous lenses besides B0128+437, namely: MG
0414+0534, B0712+472, B1359+154, B1422+231, B1555+375, B1608+656,
B1933+503, and B2045+265.  They find no strong wavelength dependence
in the flux ratios of all these systems and therefore rule out radio
propagation effects as significant contributors to the observed
anomalies.

@@

\section{Conclusions}
{\bf In this letter we have taken advantage of the power of multi-wavelength high resolution data to investigate whether flux ratio anomalies could be explained by more complex smooth models for the lens galaxy mass distribution rather than substructure. Thanks to new imaging from the SHARP $K^{\prime}$ band observations of the gravitational lens system B1555+375, we have identified the existence of a previously undetected edge-on disk. By including this disk in the mass model of the lens galaxy, we find a good fit for both the positions and flux ratios of the lensed images. Our results clearly demonstrate that the lack of knowledge on the lens galaxy mass distribution, combined with the limited information provided by the position of a few lensed images, can lead to improper lens models and a misinterpretation of the origin of flux ratio anomalies. 
We stress, therefore, that one should be very careful when interpreting the nature of flux ratio anomalies, as prior assumptions on the lens mass distribution are a significant source of bias. Finally, our analysis shows that in order to derive precise quantification of the substructure population and any derived properties from strongly lensed flux anomalous systems, it is crucial to have a careful estimation of non-substructure effects. In fact, even in the presence of mass substructures, the observed flux ratio anomalies could be still dominated by the complex structure of the lens galaxy.}
